\AtBeginSection[]{%
  \showHighlightedSectionFrame%
  }%
\frame{\titlepage}


\section{Introduction}
\begin{frame}
  \Huge \color{cscgreen} Choice...
\end{frame}
\begin{frame}{It's important, because:}
  \begin{enumerate}
    \item Build career step by step;
    \item Internships, experience;
    \item Useful acquaintances;
    \item Research projects.
  \end{enumerate}
\end{frame}

\begin{frame}{The things I like to do}
  \begin{enumerate}
    \item Prove theorems: there's a lot of fun!!!
    \item Programming (in C++, I guess).
  \end{enumerate}  
\end{frame}

\section{Some kind of research}
\begin{frame}{What does the specialist do?}
   \begin{enumerate}
     \item EDA;
     \item Prepair data;
     \item Build models;
     \item Describe your experiments in Report;
     \item Find out the best solution (you can use A/B test and e.t.c.).
   \end{enumerate}
\end{frame}

\begin{frame}{Necessary knowledge}
  \begin{enumerate}
    \item Mathematics 
      \begin{itemize}
        \item Mathematical analysis;
        \item Linear algebra;
        \item Abstract algebra;
        \item Probability theory \& statistics;
      \end{itemize}
    \item Machine learning alghorithms;
    \item Necessary Instruments.
  \end{enumerate}
\end{frame}

\section{Education \& Plans}
\begin{frame}{Mathematics?}
  Currently I study:
  \begin{enumerate}
    \item Shaposhnikov S.V., Zabotin V.I. --- mathematical analysis (MSU \& NMU lections, tasks);
    \item Shabanov D.A., Rodizhev N.E. --- probability theory;
  \end{enumerate}
\end{frame}

\begin{frame}{Programming?}
  Currently I study:
  \begin{enumerate}
    \item Vladimirov K. --- C++ basics;
  \end{enumerate}
  ML alghorithms?
  \begin{enumerate}
    \item HSE course;
    \item DL school, MIPT.
  \end{enumerate}
\end{frame}

\section{Question section}
\begin{frame}
  \Huge {\color{cscgreen} ???} Your questions {\color{cscgreen} ???}
\end{frame}

\begin{frame}
  \begin{theorem}[Very famous theorem]
    \( \sum \)
  \end{theorem}
  \begin{proof}
    Theorem Vierstreass, bluh bluh bluh ...
  \end{proof}
  \begin{remark}
    blah blah blah \Warning
  \end{remark}

\end{frame}

\begin{frame}
  \Huge {\color{cscgreen} THANK YOU FOR ATTENTION!}
\end{frame}

